%
% Daftar Pustaka 
% 

% 
% Tambahkan pustaka yang digunakan setelah perintah berikut. 
% 
\phantomsection %hack to add clickable section for pustaka
\begin{thebibliography}{4}

\bibitem{deeplearning}
{LeCun, Y., Bengio, Y., \& Hinton, G. (2015). Deep learning. Nature, 521(7553), 436–444. https://doi.org/10.1038/nature14539}

\bibitem{inception}
{Szegedy, C., Wei Liu, Yangqing Jia, Sermanet, P., Reed, S., Anguelov, D., … Rabinovich, A. (2015). Going deeper with convolutions. In 2015 IEEE Conference on Computer Vision and Pattern Recognition (CVPR). IEEE. https://doi.org/10.1109/cvpr.2015.7298594}

\bibitem{alexnet}
{Krizhevsky, A., Sutskever, I., \& Hinton, G. E. (2017). ImageNet classification with deep convolutional neural networks. Communications of the ACM, 60(6), 84–90. https://doi.org/10.1145/3065386}

\bibitem{vgg}
{Liu, S., \& Deng, W. (2015). Very deep convolutional neural network based image classification using small training sample size. In 2015 3rd IAPR Asian Conference on Pattern Recognition (ACPR). IEEE. https://doi.org/10.1109/acpr.2015.7486599}

\bibitem{ilsvrc}
{Russakovsky, O., Deng, J., Su, H. et al. Int J Comput Vis (2015) 115: 211. https://doi.org/10.1007/s11263-015-0816-y}

\bibitem{cnn}
{O'Shea, Keiron \& Nash, Ryan. (2015). An Introduction to Convolutional Neural Networks. ArXiv e-prints.}

\bibitem{tensorflow}
{Martín Abadi, dkk.. TensorFlow: Large-scale machine learning on heterogeneous systems, 2015. Software available from tensorflow.org.}

\bibitem{checkpoint}
{Saving and Restoring  |  TensorFlow. (n.d.). Retrieved December 19, 2017, from https://www.tensorflow.org/programmers\_guide/saved\_model}

\bibitem{frozengraph}
{A Tool Developer's Guide to TensorFlow Model Files  |  TensorFlow. (n.d.). Retrieved December 19, 2017, from https://www.tensorflow.org/extend/tool\_developers/\#freezing}

\bibitem{fixedquantization}
{Darryl D. Lin, Sachin S. Talathi, and V. Sreekanth Annapureddy. 2016. Fixed point quantization of deep convolutional networks. In Proceedings of the 33rd International Conference on International Conference on Machine Learning - Volume 48 (ICML'16), Maria Florina Balcan and Kilian Q. Weinberger (Eds.), Vol. 48. JMLR.org 2849-2858.}

\bibitem{floatingweightfixedactivation}
{Chandra, V., Lai, L., \& Suda, N. (2017). Deep Convolutional Neural Network Inference with Floating-point Weights and Fixed-point Activations. CoRR, abs/1703.03073.}

\bibitem{cnndroid}
{Latifi Oskouei, S. S., Golestani, H., Hashemi, M., \& Ghiasi, S. (2016). CNNdroid. In Proceedings of the 2016 ACM on Multimedia Conference - MM ’16. ACM Press. https://doi.org/10.1145/2964284.2973801}

\bibitem{caffe}
{B. (2017, November 29). BVLC/caffe. Retrieved December 20, 2017, from https://github.com/BVLC/caffe}

\bibitem{gpuenergy}
{Huang, S., Xiao, S., \& Feng, W. (2009). On the energy efficiency of graphics processing units for scientific computing. In 2009 IEEE International Symposium on Parallel \& Distributed Processing. IEEE. https://doi.org/10.1109/ipdps.2009.5160980}

\bibitem{matmulblock}
{Matsumoto, K., Nakasato, N., \& Sedukhin, S. G. (2012). Performance Tuning of Matrix Multiplication in OpenCL on Different GPUs and CPUs. 2012 SC Companion: High Performance Computing, Networking Storage and Analysis. doi:10.1109/sc.companion.2012.59}

\bibitem{convblock}
{Nugteren, C., \& Codreanu, V. (2015). CLTune: A Generic Auto-Tuner for OpenCL Kernels. 2015 IEEE 9th International Symposium on Embedded Multicore/Many-core Systems-on-Chip. doi:10.1109/mcsoc.2015.10}

\bibitem{deeplearningmatrix}
{Michael A. Nielsen, "Neural Networks and Deep Learning", Determination Press, 2015.}

\bibitem{cudagpgpu}
{Sanders, J., \& Kandrot, E. (2010). CUDA by example: An introduction to general-purpose GPU programming. Upper Saddle River: Addison-Wesley.}

\bibitem{deeplearning2}
{Lecun, Y., Bengio, Y., \& Hinton, G. (2015). Deep learning. Nature, 521(7553), 436-444. doi:10.1038/nature14539}

\bibitem{trainvsinfer}
{Nvidia White Paper. 2015. GPU-Based Deep Learning Inference: A Performance and Power Analysis}

\bibitem{tflite}
{https://www.tensorflow.org/mobile/tflite/}

\bibitem{opencl}
{Munshi, A. (2009). The OpenCL specification. 2009 IEEE Hot Chips 21 Symposium (HCS). doi:10.1109/hotchips.2009.7478342}

\bibitem{vkspec}
{Khronos Group. (2018). Vulkan: A Specification (with all registered Vulkan exstension).}

\end{thebibliography}

